6.878 Final Report

### 2013-12-10 report/paper.tex
updated paper

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=.9\textwidth]{dendrogram.png}
    \label{fig:dendrogram}
  \end{subfigure}%
  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
    %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=.9\textwidth]{wordcloud.png}
    \label{fig:wordcloud}
  \end{subfigure}%
  \label{fig:enrichment}

  \begin{subfigure}[b]{0.8\textwidth}
    \includegraphics[width=.7\textwidth]{pvalue_performace.png}
    \label{fig:pvalue}
  \end{subfigure}%
  \label{fig:enrichment}
  \caption{A) Dendrogram describing a cluster using our visualization tool. B) A word cloud generated from the clusters in the dendrogram. C) To give some performance metric, we took the ratio of the p-values for enrichment analysis for our technique over using plain k-means for the GSE675 dataset.}
\end{figure}

@@

\section{Comparison with original proposal} 
Our original proposal had many items we were going to exlplore and choose from.
We managed to complete everything that we proposed on our peer review response , including our alignment technique, several forms of clustering (Affinity Propogation, Hierarchical, K-means), several forms of enrichment analysis (DAVID's function annotations, pulling OMIM text, DAVID's gene grouping, Fischer's Exact test with multiple hypothesis corrections). We also provided a visualization tool as part of our combined class project.

\section{Commetary on experience}
Iris: I learned a lot on how to pull data and to compare results with the ones in a paper. I also learned a lot about pre-processing data and steps to take when results don't match those of the paper.

Dalesh: Working on the project was an enjoyable experience , a few highlights are as follows
a. Opportunity to work in a team and have a mentor to guide us.
b. Applying our learning on a couple of real datasets gave additional insights.
c. Structuring of the project activity with milestones starting early in the class with two interim feedback checkpoints were helpful as well.

\section{Commentary on peer-review process}
Iris: I thought that it was good to get feedback, but at the same time, our proposal was missing a lot of detail on purpose because we were not sure at the time exactly on what we were going to do, and a lot of the feedback was on lack of detail, which was not that helpful. It was nice to see other people's ideas.

Dalesh: The peer review discussion was fun but I agree with Iris's comment on the feedback we received , i recollect giving ratings on the table without having completely understood what the authors were trying to communicate and in many cases the initial proposals were in a premature stage.

\section{Division of labor}

Iris: I did some of the alignment, enrichment analysis, and clustering and helped get jobs running on Broad clusters. I also did the analysis and processing for the GSE675 dataset.

Dalesh: Most of the strategy and design was arrived at by brainstorming together , my specific implementation contributions were in data preprocessing on the amazon EC2 instances and implementations for clustering , I was responsible for processing and analyzing the GSE19392 dataset , we split the analysis of the GSE33029 dataset . Iris also did the implementations for the user interface.

\section{Acknowledgements}
Thanks to Gerald Quon, Manolis Kellis, and Maxim Wolf for their help on our project.

>>>>

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=.9\textwidth]{graphs.png}
    \label{fig:dendrogram}
  \end{subfigure}%
  ~
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=.9\textwidth]{dendrogram.png}
    \label{fig:dendrogram}
  \end{subfigure}%

  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=.7\textwidth]{wordcloud.png}
    \label{fig:wordcloud}
  \end{subfigure}%
  ~
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=.5\textwidth]{pvalue_performace.png}
    \label{fig:pvalue}
  \end{subfigure}%
  \label{fig:enrichment}
  \caption{A) The visualizer for gene expression. B) Dendrogram describing a cluster using our visualization tool. C) A word cloud generated from the clusters in the dendrogram. D) To give some performance metric, we took the ratio of the p-values for enrichment analysis for our technique over using plain k-means for the GSE675 dataset.}
\end{figure}

@@

\section{Acknowledgements}
Thanks to Peter Szolovits, Gil Alterovitz, and Gerald Quon for their help on our project.
